Test data

### 2022-07-20 Shiny/Test/Test data.Rmd
More plot and style experiments.

read_proff8 <- function(file, start, end){
    read_html(file, encoding = "UTF-8") |> 
      html_node("#inner-frame") |> 
      html_table() |> 
      select( # removing empty column
        REGNSKAPSPERIODE:all_of(start)) |> # using all_of()
      mutate( # removing whitespace
        REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
      ) |> 
      filter( # removing duplicate table - no idea why it's necessary
        !row_number() > 176
      ) |>
      filter( # removing duplicate rows
        !grepl("Lukk", REGNSKAPSPERIODE)
      ) |> 
      pivot_longer( # tidying data
        all_of(end):all_of(start), names_to = "year"
        ) |> # using all_of()
      mutate( # changing to real NAs and turning years into numbers
        value = na_if(value, "-"),
        year = as.integer(year), 
        valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
      ) |> 
      fill( # filling the currency column
        valutakode, .direction = "updown"
      ) |> 
      filter( # removing dates and redundant currency
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
          REGNSKAPSPERIODE != "Valutakode") |> 
      mutate( # removing whitespace in numbers
        value = str_replace_all(value, "\\s", ""),
        value = as.numeric(value),
        value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
      ) |> 
      distinct() |> # removing any remaining duplicate rows
      pivot_wider( # pivoting
        names_from = REGNSKAPSPERIODE, values_from = value
      ) |> 
      clean_names() |> # tidying names
      select(-lederlonn_i_hele_1000,
             -resultatregnskap_i_hele_1000,
             -balanseregnskap_i_hele_1000) |> # removing headings
      rename( # making it clear what lonn refers to
        lederlonn = lonn
      ) |> 
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |> 
      arrange(desc(year)) # arranging by year
}

@@

kreft_html5 <- read_proff8("Data/Kreftforeningen.html", "2002", "2021")

@@

>>>>

read_proff8 <- function(file, start, end){
    read_html(file, encoding = "UTF-8") |> 
      html_node("#inner-frame") |> 
      html_table() |> 
    # removing empty column
      select( 
        REGNSKAPSPERIODE:all_of(start)) |>
    # removing whitespace
      mutate( 
        REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
      ) |> 
    # removing duplicate table - no idea why it's necessary
      filter(
        !row_number() > 176
      ) |>
    # removing duplicate rows
      filter( 
        !grepl("Lukk", REGNSKAPSPERIODE)
      ) |> 
    # tidying data
      pivot_longer( 
        all_of(end):all_of(start), names_to = "year"
        ) |> 
    # changing to real NAs and turning years into numbers
    # picking out the currency
      mutate( 
        value = na_if(value, "-"),
        year = as.integer(year), 
        valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
      ) |> 
    # filling the currency column
      fill( 
        valutakode, .direction = "updown"
      ) |> 
    # removing dates and redundant currency
      filter( 
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
          REGNSKAPSPERIODE != "Valutakode") |> 
    # removing white space in numbers
    # removing years as numbers
      mutate( 
        value = str_replace_all(value, "\\s", ""),
        value = as.numeric(value),
        value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
      ) |> 
    # removing any remaining duplicate rows
      distinct() |> 
    # pivoting
      pivot_wider( 
        names_from = REGNSKAPSPERIODE, values_from = value
      ) |> 
    # tidying names
      clean_names() |> 
    # removing headings
      select(-lederlonn_i_hele_1000,
             -resultatregnskap_i_hele_1000,
             -balanseregnskap_i_hele_1000) |> 
    # making it clear what lonn refers to
      rename( 
        lederlonn = lonn
      ) |> 
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |> 
    # arranging by year
      arrange(desc(year)) 
}

@@

kreft_html_with_variables <- read_proff8("Data/Kreftforeningen.html", "2002", "2021")

@@

kreft_html_with_variables |> 
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
  geom_col() +
  scale_y_continuous(
        labels = ifelse(length(unique(kreft_html_with_variables$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(kreft_html_with_variables$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
        ) +
  scale_fill_met_d("Tsimshian",
                   direction = ifelse(
                     mean(kreft_html_with_variables$balance_positive,
                          na.rm = TRUE) == 1,-1, 1)) +
  theme(legend.position = "none") +
  labs(x = "Year", y = "", title = "Balance (in thousands)",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(kreft_html_with_variables$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
